An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-28 1_intro.tex
'beading strategy' ==> 'beading scheme'
add references in intro

\section{Introduction}
3D printing enables the fabrication of complex geometry under few design constraints compared to conventional fabrication techniques.
Recent developments have seen a rapid growth in both the use and capabilities of desktop 3D printing systems.
%The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

@@

%\subsection{Contributions}
A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
Our contributions are as follows:
\begin{itemize}
\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
\item A specific beading strategy function for this framework for:
\begin{itemize}
\item Accurately filling a 2D outline with extrusion beads
\item Reducing the overfill and underfill areas compared to the uniform width technique
\item Reducing the amount of beads with greatly deviating width compared to existing literature
\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
\end{itemize}
\end{itemize}

>>>>

\section{Introduction}
3D printing enables the fabrication of complex geometry under few design constraints compared to conventional fabrication techniques.
Recent developments have seen a rapid growth in both the use and capabilities of desktop 3D printing systems.
%The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Liu2019a}, topology optimized structures~\cite{Zong2019,Wu2019a,Cheng2019} and regular honeycomb structures~\cite{Al-Ketan2018,Maskery2018}.
Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

@@

%\subsection{Contributions}
A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
Our contributions are as follows:
\begin{itemize}
\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
\item A specific beading scheme function for this framework for:
\begin{itemize}
\item Accurately filling a 2D outline with extrusion beads
\item Reducing the overfill and underfill areas compared to the uniform width technique
\item Reducing the amount of beads with greatly deviating width compared to existing literature
\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
\end{itemize}
\end{itemize}
